BoS pilot

### 2021-12-09 code/analysis.Rmd
new pilot now with pre-chat

- why did time recording screw up for one group???

@@

##Data import constants
data_location="data/pilot211112"

date_start=lubridate::ymd('2021-11-12')

@@

# d.players <- read_csv(here(data_location, 'players.csv')) %>%
#   rename(playerId=`_id`) %>%
#   select(data.bonus, playerId,id) %>%
#   mutate(bonus=round(data.bonus,2),
#          bonus=bonus %|% 0,
#          cost=round(3.33+bonus*4/3,2)) %>%
#   write_csv(here(data_location, "player_payments.csv")) %>% select(id,bonus) %>% write_csv(here(data_location,"for_prolific.csv"))

@@

Something weird happened with time recording for Hy -- it shouldn't be possible to have times > 180 for each one, or > 120 total... Maybe it was just a time recording issue??

@@

ggplot(d.round_results, aes(x=repNum, y=time, color=playerId))+geom_point()

@@

```{r}
chat <- read_csv(here(data_location, "raw_chat.csv")) %>% filter(!is.na(text))

chat %>% group_by(gameId, playerId) %>% tally()

```
Looks like of the 5 groups:  3 talked (a little) / took longer / got more bonus and 2 didn't.

@@

```{r}
chat %>% mutate(gameId=str_sub(gameId, 0,2),playerId=str_sub(playerId, 0,2)) %>% 
  select(gameId, playerId, repNum, text) %>% kable()

@@

Player 2 prefers option B, player 1 prefers action A. In one of the non-talky games, P2 usually choose their better one.

@@

... I guess maybe we do need a free chat at the beginning so people will think they're playing with another human...

@@

>>>>

@@

##Data import constants
data_location="data/pilot211209"

date_start=lubridate::ymd('2021-12-09')

@@

# d.players <- read_csv(here(data_location, 'players.csv')) %>%
#   rename(playerId=`_id`) %>%
#   select(data.bonus, playerId,id) %>%
#   mutate(bonus=round(data.bonus,2),
#          bonus=bonus %|% 0,
#          cost=round(bonus*4/3,2)) %>%
#   write_csv(here(data_location, "player_payments.csv")) %>% select(id,bonus) %>% write_csv(here(data_location,"for_prolific.csv"))

@@

Sigh for those couple games.

@@

#ggplot(d.round_results, aes(x=repNum, y=time, color=playerId))+geom_point()

@@

pre-chat -- really we want word count not utterances, but eh. 
From skimming people do talk some. 
```{r}
#this is a sloppy way to split, but eh, 
chat <- read_csv(here(data_location, "raw_chat.csv")) %>% filter(!is.na(text)) %>% filter(is.na(targets))

chat %>% group_by(gameId, playerId) %>% tally()
```

```{r}
chat <- read_csv(here(data_location, "raw_chat.csv")) %>% filter(!is.na(text)) %>% filter(!is.na(targets))

chat %>% group_by(gameId, playerId) %>% tally() %>% full_join(d.players)

@@

```
(Full chat transcript at bottom)

@@

Player 2 prefers option B, player 1 prefers action A.

@@

@@

```
# Chat

```{r}
read_csv(here(data_location, "raw_chat.csv")) %>% filter(!is.na(text)) %>% mutate(gameId=str_sub(gameId, 0,2),playerId=str_sub(playerId, 0,2)) %>% 
  select(gameId, playerId, repNum, text) %>% kable()
